\section{Data} \label{data-section}

The electoral data comes from the French Ministry of the Interior. Municipality characteristics are from the French censuses of 1990, 1999, and 2007. Table \ref{tab:descriptive} reports descriptive statistics of the control variables in 1990, all of which are known to influence electoral behavior. Additionally, we gathered geographical characteristics of municipalities, such as altitude and size of the area. We computed the distance to the closest agglomeration (defined as a locality with a population size in 1990 above the 9th decile of the overall population size distribution in 1990). Using satellite data from the National Geographic Institute \citep{IGN2020}, we also collected information on the density of fences (haie) to measure bocage areas and the density of vines for wine-producing regions. Lastly, we obtained data on the density of Organizations of Public Interest (OPI) from the \textit{Journal officiel des associations et fondations d'entreprise} (JOAFE) as a measure of Social Capital (in the sense of \cite{putnam2000}).

The data construction is performed at the commune level. Because French commune and canton codes can change over time, we audit all commune-code joins and the 1999 canton bridge before estimating the models. The bridge file used in the project has the structure of an INSEE \textit{Code officiel géographique} commune-history file and contains several hundred communes split across multiple canton rows. We therefore do not assign those communes to the first listed canton. Instead, the pipeline gives split-canton communes and communes with missing canton codes their own commune-specific cluster identifiers and reports exclusion sensitivities. This convention prevents silent row multiplication and avoids pretending that every commune has a unique verified historical canton. The remaining limitation is provenance: the exact original download URL for the local 1999 bridge file is not yet recovered, so the replication package documents this as an assumption and keeps the split-canton sensitivity checks visible.

% Descriptive Statistics
\input{tables/descriptive_statistics.tex}


The first notable element is that the proportion of agricultural workers is significantly higher in the municipalities treated in 1995. Additionally, these municipalities have smaller populations, more OPIs per capita, fewer manual workers (ouvriers), they experienced the harshest negative employment shock between 1982 and 1990, saw their population decreased between 1982 and 1990, and are situated at higher altitudes.
